---
title: "In Class PGA Regression Exercise"
author: "Brian Wright"
date: "March 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Try to develop a model that predicts total winnings using the same techniques we just reviewed: 
Check Assumptions: Linear relationship between dep and indeps (plots), normal predictor variables (skewness, shapiro), non-correlation (VIF) and consistant errors (nvcTest)
Create a model using lm()
Use the model to create predict values and if you have time develop a RSME
We are going to us data located on a website here:http://www.stat.ufl.edu/~winner/data/pga2004.dat with information on the dataset located here:http://www.stat.ufl.edu/~winner/data/pga2004.txt
Use the data.table package to get your data into R then develop a initial model
```{r, echo=TRUE}
library(data.table)
pgadata <- fread("http://www.stat.ufl.edu/~winner/data/pga2004.dat", fill = TRUE)
head(pgadata)
str(pgadata)
names(pgadata) <- c("First", "Last","Age","AveDrive","DriveAccur","GreensReg","AvePuts","Save%","MoneyRank","NoEvents","TotalWin","AverWin","NA")
head(pgadata)
```

